---
title: "Visualization and EDA"
author: "Vanessa Dinh"
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Let's Import Data

```{r set_up}
library(tidyverse)
library(ggridges)
```

# Example
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
weather_df
```

# Basic scatterplot
```{r}
ggplot(weather_df, aes(x = tmin, y = tmax))
```

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point()
```
```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point()
```

```{r}
plot_weather = 
  weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) 

plot_weather + geom_point()
```

# Advanced Scatterplot

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name))
```
```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name), alpha = .5) +
  geom_smooth(se = FALSE)
```

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax, color = name)) + 
  geom_point(alpha = .5) +
  geom_smooth(se = FALSE) + 
  facet_grid(. ~ name)
```
```{r}
ggplot(weather_df, aes(x = date, y = tmax, color = name)) + 
  geom_point(aes(size = prcp), alpha = .5) +
  geom_smooth(se = FALSE) + 
  facet_grid(. ~ name)
```

# Learning Assessment
```{r}
weather_df %>% 
  filter(name == "CentralPark_NY") %>% 
  mutate(
    tmin_fahr = tmin * (9/5) + 32,
    tmax_fahr = tmax * (9/5) + 32) %>% 
  ggplot(aes(x = tmin_fahr, y = tmax_fahr)) +
    geom_point(alpha = 0.5) +
    geom_smooth(method = "lm", se = FALSE)
```

# Odds and Ends

```{r}
ggplot(weather_df, aes(x = date, y = tmax, color = name)) + 
  geom_smooth(se = FALSE) 
```

```{r}
ggplot(weather_df, aes(x = tmax, y = tmin)) + 
  geom_hex()
```

```{r}
ggplot(weather_df) + geom_point(aes(x = tmax, y = tmin), color = "blue")
ggplot(weather_df) + geom_point(aes(x = tmax, y = tmin, color = "blue"))
```
color = "blue" is outside of the aes() in the first and inside aes() in the second
creating color to geom_point by hand in the first, creating a variable with the value "blue" in the second

# Univariate plots ...

Histograms, barplots, boxplots, violins, ...

```{r}
ggplot(weather_df, aes(x = tmax)) + 
  geom_histogram()
```
```{r}
ggplot(weather_df, aes(x = tmax, fill = name)) + 
  geom_histogram(position = "dodge", binwidth = 2)
```
fill is better than color = for histograms
"dodge" is better than default position

```{r}
ggplot(weather_df, aes(x = tmax, fill = name)) + 
  geom_density(alpha = .4, adjust = .5, color = "blue")
```

alpha codes for transparency

```{r}
ggplot(weather_df, aes(x = name, y = tmax)) + geom_boxplot()
```
```{r}
ggplot(weather_df, aes(x = name, y = tmax)) + 
  geom_violin(aes(fill = name), alpha = .5) + 
  stat_summary(fun = "median", color = "blue")
```
```{r}
ggplot(weather_df, aes(x = tmax, y = name)) + 
  geom_density_ridges(scale = .85)
```
# Learning Assessment

```{r}
ggplot(weather_df, aes(x = prcp, fill = name)) +
  geom_histogram(position = "dodge", binwidth = 10)
```
```{r}
ggplot(weather_df, aes(x = prcp)) +
  geom_density(aes(fill = name), alpha = .5)
```
```{r}
ggplot(weather_df, aes(x = prcp, y = name)) + 
  geom_density_ridges(scale = .85)
```


```{r}
ggplot(weather_df, aes(y = prcp, x = name)) + 
  geom_boxplot() 
```
# Saving and Embedding Plots

```{r}
weather_plot = ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name), alpha = .5) 

ggsave("weather_plot.pdf", weather_plot, width = 8, height = 5)

weather_plot
```
```{r}
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
```

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name))
```


